\textbf{Appendix}\\ Bound within Boundaries: How Well Do Protected Areas Match Movement Corridors of Their Most Mobile Protected Species?

### 2020-09-21 Chapter_0/04_Manuscript/Manuscript_Support.tex
Worked on revisions
Finalized revisions

%------------------------------------------------------------------------------
%	Appendix S1: Net Squared Displacement
%------------------------------------------------------------------------------
\section{Net Squared Displacement}\todo{Reviewer 1 pointed out that we need to
replace calssified with classified}
\begin{figure}[hbpt]
  \begin{center}
    \includegraphics[width = \textwidth]{99_NSD.pdf}
    \caption{NSD displacement through time for one of our dispersers. The blue
    line indicates the period during which we classified the individual as
    dispersing.}
    \label{NSD}
  \end{center}
\end{figure}

@@

\begin{table}[hbtp]
  \caption{Summary statistics of all GPS relocations that have been recorded on
  dispersing coalitions.}
  \label{GPSData}
  \begin{center}
    \resizebox{0.8\textwidth}{!}{
      \begin{tabular}{lccccccc}
      \toprule
      \parbox[]{2cm}{\centering Coalition ID} &
        \parbox[]{1cm}{\centering Sex} &
          \parbox[]{2cm}{\centering \ Pack \\ Affiliation} &
            \parbox[]{1.5cm}{\centering \# Fixes \\ Total} &
              \parbox[]{1.5cm}{\centering \# Fixes \\ During \\ Dispersal} &
                \parbox[]{1.5cm}{\centering \# Days \\ Dispersing} &
                  \parbox[]{2cm}{\centering Euclidean \\ Dispersal\\ Distance \\ (in km)} &
                    \parbox[]{2cm}{\centering Cumulative \\ Dispersal \\ Distance \\ (in km)} \\
      \midrule
      Abel & M & MU & 894 & 45 & 9 & 131 & 205 \\
      Amacuro & F & MB & 954 & 583 & 137 & 23 & 1'090 \\
      Belgium & M & ZU & 1'097 & 158 & 28 & 18 & 319 \\
      Dalwhinnie & F & PA & 545 & 62 & 22 & 50 & 243 \\
      Denali & F & MN & 1'096 & 173 & 33 & 11 & 528 \\
      Everest & M & MN & 389 & 123 & 38 & 67 & 572 \\
      Kalahari & F & HT & 1'753 & 467 & 130 & 20 & 1'963 \\
      Karisimbi & M & MN & 438 & 141 & 34 & 45 & 251 \\
      Liuwa & F & AP & 946 & 92 & 19 & 144 & 451 \\
      Lupe & M & KW & 2'209 & 396 & 34 & 8 & 436 \\
      MadameChing & F & AP & 776 & 729 & 136 & 263 & 1'560 \\
      Mirage & M & HT & 814 & 182 & 36 & 7 & 435 \\
      Odzala & M & AP & 1'410 & 205 & 42 & 53 & 412 \\
      Scorpion & M & KB & 2'676 & 393 & 34 & 4 & 471 \\
      Stetson & M & MT & 384 & 383 & 33 & 3 & 481 \\
      Taryn & F & AP & 896 & 37 & 9 & 10 & 130 \\
      \toprule
      \toprule
      \textit{Mean} & - & - & 1080 & 261 & 48 & 54 & 597 \\
      \textit{(SD)} & - & - & (649) & (207) & (44) & (71) & (508) \\
      \bottomrule
      \end{tabular}
    }
  \end{center}
\end{table}

@@

\subsection{Human Influence}
We created a raster layer representing human influence by integrating
information on (1) human density, (2) farming, and (3) roads.

@@

\begin{table}[hbtp]
  \begin{center}
    \caption{Overview of spatial covariates and their sources. We extracted
    covariates along realized and random steps. For continuous covariates we
    calculated average values along steps, for categorical covariates the
    percentage coverage along steps. We also prepared two covariates indicating
    the distance to water and distance to roads, respectively. We square-rooted
    the values for these two covariates to render a decreasing marginal impact
    of the effect of distance. Finally, we derived a binary indicator of whether
    a step crossed a road or not.}
    \label{Appendix:Sources}
    \resizebox{\textwidth}{!} {
      \begin{threeparttable}
        \begin{tabular}{lllll}
        \hline
        Category &
          Covariate &
            Description &
              Values &
                Source \\
        \midrule
        \multirow{5}{*}{Land Cover}
          & Water
            & Percentage cover of water
              & 0-100\%
                & (1) (2) (3) \\
          & Dryland*
            & Percentage cover of dryland
              & 0-100\%
                & (1) (2) (3) \\
          & DistanceToWater
            & Average distance to nearest water source
              & \(\geq\) 0m
                & (1) (2) (3) \\
          & Shrubs/Grassland
            & Average non-tree vegetation
              & 0-100\%
                & (4) \\
          & Trees
            & Average tree-vegetation
              & 0-100\%
                & (4) \\
          & Bareland*
            & Average non-vegetated area
              & 0-100\%
                & (4) \\
        \hdashline
        \multirow{2}{*}{Protection Status}
          & Protected
            & Percentage cover of protected area
              & 0-100\%
                & (5) \\
          & Unprotected*
            & Percentage cover of unprotected area
              & 0-100\%
                & (5) \\
        \hdashline
        \multirow{3}{*}{Human Influence}
          & Human Influence
            & Average human influence
              & \(\geq\) 0
                & (1) (6) (7) (8)\\
          & DistanceToRoads
            & Average distance to nearest road
              & \(\geq\) 0m
                & (1) (6) (7) (8)\\
          & RoadCrossing
            & Binary; whether a step crossed a road
              & 0, 1
                & (1) (6) (7) (8)\\
        \hline
        \end{tabular}
        \begin{tablenotes}
          \item \textit{Sources:} (1) \cite{Chen.2015} (2) \cite{Schaaf.2015} (3)
          \cite{Yamazaki.2019} (4) \cite{Dimiceli.2015} (5) \cite{PeaceParks.2019}
          (6) \cite{Facebook.2019} (7) \cite{OpenStreetMap.2019} (8)
          \cite{Xiong.2017}
          \item
          \item \textit{* Note:} The covariates \textit{Water} and
          \textit{Dryland} added up to 100\%, which is why only \textit{Water} was
          included as explanatory variable in our models. The same applied for the
          group \textit{Shrubs/Grassland}, \textit{Trees}, and \textit{Bareland},
          where we omitted \textit{Bareland} for modeling. Finally, from the group
          \textit{Protected} and \textit{Unprotected}, we only included
          \textit{Protected} in our models.
        \end{tablenotes}
      \end{threeparttable}
    }
  \end{center}
\end{table}

>>>>

%------------------------------------------------------------------------------
%	Appendix S1: Net Squared Displacement
%------------------------------------------------------------------------------
\section{Net Squared Displacement}

\begin{figure}[hbpt]
  \begin{center}
    \includegraphics[width = \textwidth]{99_NSD.pdf}
    \caption{NSD displacement through time for one of our dispersers. The blue
    line indicates the period during which we classified the individual as
    dispersing.}
    \label{NSD}
  \end{center}
\end{figure}

@@

\begin{table}[hbtp]
  \caption{Summary statistics of all GPS relocations that have been recorded on
  dispersing coalitions.}
  \label{GPSData}
  \begin{center}
    \resizebox{\textwidth}{!}{
      \begin{tabular}{lccccccc}
      \toprule
      \parbox[]{2cm}{\centering Coalition ID} &
        \parbox[]{1cm}{\centering Sex} &
          \parbox[]{2cm}{\centering \ Pack \\ Affiliation} &
            \parbox[]{1.5cm}{\centering \# Fixes \\ Total} &
              \parbox[]{1.5cm}{\centering \# Fixes \\ During \\ Dispersal} &
                \parbox[]{1.5cm}{\centering \# Days \\ Dispersing} &
                  \parbox[]{2cm}{\centering Euclidean \\ Dispersal\\ Distance \\ (in km)} &
                    \parbox[]{2cm}{\centering Cumulative \\ Dispersal \\ Distance \\ (in km)} \\
      \midrule
      Abel & M & MU & 894 & 45 & 9 & 131 & 205 \\
      Amacuro & F & MB & 954 & 583 & 137 & 23 & 1'090 \\
      Belgium & M & ZU & 1'097 & 158 & 28 & 18 & 319 \\
      Dalwhinnie & F & PA & 545 & 62 & 22 & 50 & 243 \\
      Denali & F & MN & 1'096 & 173 & 33 & 11 & 528 \\
      Everest & M & MN & 389 & 123 & 38 & 67 & 572 \\
      Kalahari & F & HT & 1'753 & 467 & 130 & 20 & 1'963 \\
      Karisimbi & M & MN & 438 & 141 & 34 & 45 & 251 \\
      Liuwa & F & AP & 946 & 92 & 19 & 144 & 451 \\
      Lupe & M & KW & 2'209 & 396 & 34 & 8 & 436 \\
      MadameChing & F & AP & 776 & 729 & 136 & 263 & 1'560 \\
      Mirage & M & HT & 814 & 182 & 36 & 7 & 435 \\
      Odzala & M & AP & 1'410 & 205 & 42 & 53 & 412 \\
      Scorpion & M & KB & 2'676 & 393 & 34 & 4 & 471 \\
      Stetson & M & MT & 384 & 383 & 33 & 3 & 481 \\
      Taryn & F & AP & 896 & 37 & 9 & 10 & 130 \\
      \toprule
      \toprule
      \textit{Mean} & - & - & 1'080 & 261 & 48 & 54 & 597 \\
      \textit{(SD)} & - & - & (649) & (207) & (44) & (71) & (508) \\
      \bottomrule
      \end{tabular}
    }
  \end{center}
\end{table}

@@

\subsection{Anthropogenic}
We created a raster layer representing human influence by integrating
information on (1) human density, (2) farming, and (3) roads.

@@

\begin{table}[hbtp]
  \begin{center}
    \caption{Overview of spatial covariates and their sources. We extracted
    covariates along realized and random steps. For continuous covariates we
    calculated average values along steps, for categorical covariates the
    percentage coverage along steps. We also prepared two covariates indicating
    the distance to water and distance to roads, respectively. We square-rooted
    the values for these two covariates to render a decreasing marginal impact
    of the effect of distance. Finally, we derived a binary indicator of whether
    a step crossed a road or not.}
    \label{Appendix:Sources}
    \resizebox{\textwidth}{!} {
      \begin{threeparttable}
        \begin{tabular}{lllll}
        \hline
        Category &
          Covariate &
            Description &
              Values &
                Source \\
        \midrule
        \multirow{5}{*}{Land Cover}
          & Water
            & Percentage cover of water
              & 0-100\%
                & (1) (2) (3) \\
          & Dryland*
            & Percentage cover of dryland
              & 0-100\%
                & (1) (2) (3) \\
          & DistanceToWater
            & Average distance to nearest water source
              & \(\geq\) 0m
                & (1) (2) (3) \\
          & Shrubs/Grassland
            & Average non-tree vegetation
              & 0-100\%
                & (4) \\
          & Trees
            & Average tree-vegetation
              & 0-100\%
                & (4) \\
          & Bareland*
            & Average non-vegetated area
              & 0-100\%
                & (4) \\
        \hdashline
        \multirow{2}{*}{Protection Status}
          & Protected
            & Percentage cover of protected area
              & 0-100\%
                & (5) \\
          & Unprotected*
            & Percentage cover of unprotected area
              & 0-100\%
                & (5) \\
        \hdashline
        \multirow{3}{*}{Anthropogenic}
          & Human Influence
            & Average human influence
              & \(\geq\) 0
                & (1) (6) (7) (8)\\
          & DistanceToRoads
            & Average distance to nearest road
              & \(\geq\) 0m
                & (1) (6) (7) (8)\\
          & RoadCrossing
            & Binary; whether a step crossed a road
              & 0, 1
                & (1) (6) (7) (8)\\
        \hline
        \end{tabular}
        \begin{tablenotes}
          \item \textit{Sources:} (1) \cite{Chen.2015} (2) \cite{Schaaf.2015}
          (3) \cite{Yamazaki.2019} (4) \cite{Dimiceli.2015} (5)
          \cite{PeaceParks.2019} (6) \cite{Facebook.2019} (7)
          \cite{OpenStreetMap.2019} (8) \cite{Xiong.2017}
          \item
          \item \textit{* Note:} The covariates \textit{Water} and
          \textit{Dryland} added up to 100\%, which is why only \textit{Water}
          was included as explanatory variable in our models. The same applied
          for the group \textit{Shrubs/Grassland}, \textit{Trees}, and
          \textit{Bareland}, where we omitted \textit{Bareland} for modeling.
          Finally, from the group \textit{Protected} and \textit{Unprotected},
          we only included \textit{Protected} in our models.
        \end{tablenotes}
      \end{threeparttable}
    }
  \end{center}
\end{table}
